### 2023-11-03 Scripts/Manuscript/manuscript.Rmd
added the measurement section text, but not yet the formulas and table. Also solved an issue with the renv not being up to date.

As a response, the demand to verify the credibility of psychological findings through replications rose. In order to attempt replications of various psychological findings, numerous large scale projects were set-up [@klein2014data; @camerer2016evaluating; @camerer2018evaluating; @ebersole2016many; @ebersole2020many; @klein2018many; @klein2022many}. Among these were the Many Labs projects, which operated similarly to the RPP, with the additional feature that each original article was replicated multiple times across different labs in various locations around the world. The results from these replication projects generally showed smaller effects than those reported in the original studies. Similarly, effects that had reached statistical significance in the original no longer did across the aggregate results of its replications.

@@

## Questionable Measurement Practices
@flake2022construct descriptively investigated QMPs within the reproducibility project psychology [@osc2015estimating]. This thesis seeks to conceptually replicate some of their findings within the Many Labs replication projects.

@@

@@

@@

@@

@@

@@

## Measures

### Measurement Error Measures

### Replicability Measure

### QMP measures

### Validity Measure

## Analyses

### Analyses Measurement Error

### Analyses QMPs

### Exploratory Analyses

>>>>

As a response, the demand to verify the credibility of psychological findings through replications rose. In order to attempt replications of various psychological findings, numerous large scale projects were set-up [@klein2014data; @camerer2016evaluating; @camerer2018evaluating; @ebersole2016many; @ebersole2020many; @klein2018many; @klein2022many]. Among these were the Many Labs projects, which operated similarly to the RPP, with the additional feature that each original article was replicated multiple times across different labs in various locations around the world. The results from these replication projects generally showed smaller effects than those reported in the original studies. Similarly, effects that had reached statistical significance in the original no longer did across the aggregate results of its replications.

@@

@flake2022construct descriptively investigated QMPs within the reproducibility project psychology [@osc2015estimating]. This thesis seeks to conceptually replicate some of their findings within the Many Labs replication projects.

@@

Data collection, coding protocol, and planned analyses were all preregistered. The preregistration and supplementary materials can be found on this thesis' OSF page: <https://osf.io/9r8yt/>. Any deviations from the preregistration are explicitly mentioned in the text.

@@

The data used for the analyses in this thesis consists of three main sources: replication datasets, preregistered replication protocols, and original study articles. The data came from the Many Labs series of studies. In particular, data from Many Labs 1, 2, 3, & 5 was used [@klein2014data; @klein2018many; @ebersole2016many; @ebersole2020many]. Data from Many Labs 4 [@klein2022many] was not part of the sample, as there was no publicly available protocol which contains the information needed to code QMPs. Additionally, the replication of [@crosby2008we] in Many Labs 5 did not contain contain data suitable for this project. The replication made use of videos and eye-tracking as measures, which does not match this thesis' focus on scale and item measures.

The total number of psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of 60: 13 in Many Labs 1; 28 in Many Labs 2; 10 in Many Labs 3; & finally 9 out of the 10 tested findings in Many Labs 5. Since each replication set is related to an original study, the number of effects in original studies matches the number of effects in replication research.

However, the unit of measurement was not a single study or replication. Instead each measure of a unique variable within a Many Labs project was treated as the unit of measurement. The reason being that studies could have and did use multiple measures. Additionally, measures can assess multiple dimensions. These dimensions, meaning unique variables, were separated into different units whenever possible, otherwise the measure was discarded from analysis. However, not all measures of unique variables were used. Only data from measures of primary variables, meaning those variables included in the primary test of the replication, were used. This was done to ensure that the analyses could link directly to the replicability of a study. Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included. The result was a total sample size of 77 measures: 14 in Many Labs 1; 35 in Many Labs 2; 15 in Many Labs 3; & 13 in Many Labs 5. Again, the sample was equivalent between replications and original studies.

@@

The replication datasets refer to the data of each of the replication attempts for each of the original psychological effects undertaken as part of a Many Labs study. The specific data was extracted from the replication datasets for each relevant measure. The measure had to consist of multiple scalar items to be considered relevant for the related analyses. Single item measures were not usable for the analyses on score reliability [@wanous1996estimating] as they do not translate directly to the findings of @stanley2014expectations, which this thesis is following up on.

For Many Labs 1, all the relevant replication data was available in a single csv file. For Many Labs 2 & 3 the situation was similar, only here the files were split across two csv files for each project. For Many Labs 5, the data was made available for each of the ten replication sets separately. Three out of the ten datasets were furthermore split across the various locations at which they were taken. If cleaned data was available this was chosen over raw data. Pilot data were omitted from the analyses entirely. This resulted in suitable measure data from eighteen replication sets spread across on average 40 lab locations for the analyses of hypotheses 2 & 3.

@@

The preregistered replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each replication set. These protocols were available through the OSF pages of each Many Labs project. These preregistered replication protocols, as well as the replication datasets mentioned earlier were scanned through to ensure that the planned analyses were feasible. However, no coding or analysis of either of them had taken place before the analyses were preregistered. This includes any systematic coding of the QMPs present in the report. Furthermore, no overview of these and the qualitative topics were available at the time of preregistration.

Finally, the reports of the Many Labs projects, meaning the published articles [@klein2014data; @klein2018many; @ebersole2016many; @ebersole2020many], were used to determine whether not the replication was considered successful.

@@

The original study articles are the published articles of the original effect on which the Many Labs replication sets were based. In the case of Many Labs 5 the original studies refer to the studies which first tested the effect to be replicated, not the earlier replication attempts of the same effects in the RPP [@osc2015estimating].

@@

The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. When available, codebooks and study materials were used to identify the specific data for each measure.

The publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@Posit2023RStudio] with R version 4.2.2 [@R2021R]. Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each measure were extracted into their own data frame containing the data from all studies in one replication set. These pieces of information formed the replication datasets in the analysis.

The OSF page for each Many Labs project was combed through, in order to identify the components of the research which contained information on the measurement practice and reported reliability. The focus was on finding the preregistered protocols which contained information on the entirety of the replication sets in each Many Labs project. This was successful for Many Labs 2, & 3. For Many Labs 1 the Proposal_V1.1 was selected as the proper candidate for the QMP analysis. Despite the difference in name, it is the equivalent in Many Labs 1 to the protocols of Many Labs 2 & 3. For Many Labs 5 the protocols were made accessible for each replication set separately. The relevant OSF page of each replication set was searched through for a file which contained protocol in its name. If available, a version of the protocol labelled as revised, post-review, peer-review, or endorsed was selected. In case there was doubt about which was most appropriate, the latest uploaded relevant protocol was selected. Only regular protocols were taken, meaning those not labelled as data collection, analysis protocol or anything similar[^1].

[^1]: The steps taken to access the replication protocol data from Many Labs 5 were not preregistered, and only became clear upon further investigation of the accessible information. The specific names and locations of the files that were used as the datasets can be found under the supplementary materials of the OSF page of this thesis <https://osf.io/gft46/%7D>

The original articles were identified through the citations in each replication protocol, using Web of Science, Google Scholar, and PsychInfo (in that order). An issue was encountered while trying to access @hyman1950current. However, after contacting the first author of @klein2014data a suitable version of the article was obtained for use in the analyses.

The measures of primary variables were identified by combing through the entire methods section of each preregistered replication protocols. Then using the structured coding protocol (made using Qualtrics) available on the OSF page for this thesis (<https://osf.io/9r8yt/>), each measure of a unique variable was coded on measurement reporting and reported reliability.

The structured coding protocol was used for both replication protocols and original studies. A series of questions relating to measurement practices and measurement error were used to extract the information. Descriptions of the extracted variables can be found in the Measures section below. The scope of the coding was limited to the abstract, method, procedure, materials, measure, and initial parts of the results sections. Additionally, a keyword search using the name of the measured variable was used to search for any potentially missed information. An exception to this procedure was a question asking about the presence of example items. For this question, information from supplementary materials was uniquely considered as relevant. Another exception was the question regarding the replication of the original effect. Tables from the final report of each Many Labs project were used to answer that question.

<!-- \@ref(sec:measures) didn't work for section corss-reference in the paragraph above-->

After the data was initially coded according to the preregistered coding protocol, it was determined, based on discussion with the supervisor, that some of the initial ratings were possibly to stringent. As a result, some of the items in the protocol were reformulated, so that the conclusions from the resulting analyses were based on a more favourable judgement of QMPs. These changes included: accepting linked online appendices as a data source for example items; assuming that if no differences between replication and original are measurement is mentioned, that there is no difference, even if it is not explicitly clear; and generally simplified criteria for what constituted sufficiently clear reporting. The revision of the coding protocol happened after all the data were coded using the initial protocol. As a result the coded data using the initial protocol, and the coded data using the revised protocol are both available available on this thesis' OSF page: <https://osf.io/9r8yt/>. Both raw and processed formats are present.

## Measures {#sec:measures}

### Measurement Error Measures
Two main sources of information were used to test hypothesis 1, the reported reliability coefficient from the replication protocols, and the reported reliability coefficient in the original articles. The reported reliability coefficient is the score reliability reported per measure in the replication protocol or original article. Both the type (Cronbach's alpha, retest, interrater, etc.) and the value itself were extracted.

The test of hypothesis 2 was based on different score reliabilities. As stated earlier, only score reliabilities of scalar measures with multiple items were included in the test of hypothesis 2. Because data was available for each lab location within a replication set, it was possible to calculate score reliabilities of a measure for each lab location. With location specific score reliabilities, it was possible to assess the variation of score reliabilities of the same measure across different contexts.

Two different types of score reliabilities were calculated: Cronbach's alpha and omega. Cronbach's alpha was used as it is one of the most popular indices of score reliability [@cho2015cronbach]. Omega was added to the analysis as it has been argued to be a more informative measure of score reliability, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing]. Cronbach's alpha and omega were calculated using the alpha and omega functions respectively in the psych R package [@revelle2022psych]. Default arguments were used for both functions except the nfactors in the omega function, which was set to 1.

### Replicability Measure
Hypothesis 3 as well as 5 specify an association between either score reliability or QMPs respectively, and replication success. Replication success was based on the test of the main effect of a study. However, the unit of measurement for the data in this thesis was a measure of a unique variable, not an effect. Fortunately, since only primary measures were included in the data, each measured a variable of the main effect, and as a result the measure remains related to the test of the main effect. Replication was based on the significance of the meta-analytic effect of the replication set as reported in its respective Many Labs report. An effect was considered replicated if the meta-analytic p-value was lower than .05, and in the same direction as the original effect. In all cases, meta-analytic significance of an effect meant that support in the direction of the original effect was found.

The tests for hypotheses 4, 5, & 6 were all based on the number of QMPs per category that were determined by the research using the coding protocol. An overview of the QMP categories of the coding variables, based on @flake2020measurement, can be seen in Table INSERT TABLE 1 REF HERE

INSERT TABLE 1 HERE

Selection and creation share a category as the justifications and requirements in selecting a measure are similar to those for creating a new measure. Modification variables were only assessed when it was clear that the measure was modified from an original source in some way. The questions were all answered as either true, false, or not applicable. Questions related to modification had 'no modification' as an additional answer option, in case the specific aspect of the measure was explicitly not modified. Beside these quantitative variables, a total of four qualitative variables were also included to measure details surrounding measurement practices. These variables assessed: the specific version of the measure (if reported); whether and what previous materials were used for the study; what, if any, psychometric evidence beyond reliability score (e.g. factor analysis, IRT model, convergent validity) was provided; and whether it was specified or not that the measure was or was not modified.

Two of the qualitative items have an equivalent in the coding key of @flake2022construct. Eleven out of twenty of the quantitative coding variables have an equivalent in @flake2022construct. Variables related to the specific measurement scaling and purpose in the paper, were omitted from the analyses of this thesis as they were deemed neither relevant for the analyses of this study, nor necessary in matching this study to the key results of @flake2022construct. Questions about more general measurement features such as the number of items and how scores were aggregated were altered from @flake2022construct to better fit the aims of this thesis.

The tests for hypotheses 4, 5, & 6 were all based on QMP ratios, both total QMP ratios and ratios per QMP type. This ratio was based on the number of coded trues divided by the number of applicable QMPs. When a question was coded as true, this equated to a count of one QMP for that type and in total, whereas false equated to a zero. If coded as not applicable or no modification (for the modification items), this item was considered not applicable. Non applicable responses were not only counted as a zero, but additionally the denominator for calculating the ratio of QMPs was lowered by one. These ratios were preferred over counts, since non applicable items could thus be accounted for.

### QMP measures
The same data as for the test of hypothesis 2 was used to check for the unidimensionality of the factor structure, as part of the exploratory analyses. A check for unidimensionality as validity evidence only makes sense if the measure was intended to be unidimensional. Therefore, for each replication for which data was available, the protocol was checked to ensure that the scores on each measure were meant to assess a single construct.

### Validity Measure
The same data as for the test of hypothesis 2 was used to check for the unidimensionality of the factor structure, as part of the exploratory analyses. A check for unidimensionality as validity evidence only makes sense if the measure was intended to be unidimensional. Therefore, for each replication for which data was available, the protocol was checked to ensure that the scores on each measure were meant to assess a single construct.

## Analyses
### Analyses Measurement Error
Every hypothesis test in this thesis used an alpha significance cutoff of .05. No correction for multiple testing was applied, to avoid inflating type II error rate. The generally small sample size and consequently low power of these analyses meant that a smaller alpha would increase the number of false negatives. On top of that, these analyses were considered as exploratory. In this exploratory context, the rate of discovery of any potential true effects was given more value relative to decreasing any false positives compared to typical confirmatory research. That as a consequence obtaining false positives was more likely has been accepted, as false negatives were deemed more harmful to this study's aims.

The measurement error analyses testing hypotheses 1, 2, & 3 deviated from the preregistration for two main reasons: there were too few reported reliability coefficients, and too few multiple item scalar measures to calculate the reliability coefficients from. Because of the small sample size, the test for hypothesis 1 was changed, and the low power as a result of the sample size was accepted for hypothesis 2 & 3. This should be kept in mind while interpreting the results from these hypothesis tests.

Thus for testing hypothesis 1, instead of comparing the reported Cronbach's alpha coefficient between original and replication, the total number of reported reliability coefficients were compared instead. This total also included reliability coefficients other than Cronbach's alpha. This comparison was implemented via a chi-square test using the base R stats package [@R2021R].

The number of usable datasets to calculate reliability coefficients from was similarly limited in number. However, the number of datasets were still sufficient to be able to estimate the models of the planned analysis for hypothesis 2, albeit with a more exploratory goal than intended.

Using the lmer function from the lme4 package [@bates2015lme4], a multilevel null model with the Cronbach's alpha or omega coefficient of a replication as dependent was specified, where the random intercept was grouped by replication set. The formulas for this model, where $alpha_{ij}$ represents the calculated Cronbach's alpha coefficient of a single study at one lab location with $i = 1,..., n_{locations}$ and $j = 1,...,n_{replications}$ look as follows:

INSERT H2 FORMULA HERE

The purpose of this analysis was to investigate variability in calculated reliability coefficients within and between replication sets. However, to the author’s knowledge no formal test exists as of the writing of this thesis for testing the significance of within group variance after controlling for between group variance. Instead the intraclass correlation (ICC) coefficient was calculated an indicator of within vs. between variability. Formula XXX shows the formula used to calculate the ICC.

INSERT ICC FORMULA HERE

A high ICC indicates low within group variance relative to between group variance, which would be in line with hypothesis 2.

In order to test hypothesis 3, the average calculated Cronbach's alpha level within a replication set is used as a predictor of replication success. Replication success was either set to 1 if it reached meta analytic significance at an alpha of .05 in the same direction as that found in the original study, or 0 otherwise. This test aligns with a logistic regression model. With $i = 1,..., n_{replications}$, $p_{replicated}$ being binomially distributed, and $alpha$ referring to the averaged calculated Cronbach's alpha coefficient, the following regression equation was used to model the relation:

INSERT H3 FORMULA HERE

Where:

INSET f(.) FORMULA HERE

In this data, replication attempts at different lab locations can be seen as nested within a replication set. In order to see if this nesting might impact the analyses of hypothesis 3, multilevel logistic regression models were included as sensitivity checks. The dependent variable remains replication success at the replication set level, while Cronbach's alpha is no longer averaged across locations. The models used were a multilevel logistic random intercept and random slope model.

### Analyses QMPs
The reported analyses were primarily based on the revised set of QMP data. The results using the original QMP data are mentioned when the results led to different conclusions. The analysis code for both the original and revised QMP data are available in R script on the OSF page of this thesis: <https://osf.io/9r8yt/>.

Hypothesis 4, 5, & 6 were all tested using a model with the same dependent variable: total QMP ratio. In order to model a ratio dependent variable, beta regression was used. Beta regression models operate similarly to standard generalized linear models with similar interpretations of the results. What differentiates them is that they are suitable to model dependent variables with values in the interval of $(0, 1)$, meaning ratios. Furthermore, they are well suited for modelling heteroskedastic and asymmetrically distributed dependent variables [@cribari2010beta]. The beta regression model was implemented using the betareg function within the betareg package [@cribari2010beta]. Defaults were used for all function parameters besides the model formula and data. All beta regression models used the beta link function, which is as follows:

INSERT BETALINK FORMULA HERE

All of these models assume that the QMPs are the same across each replication set. The reason being that only one protocol was analysed per replication set, and several of the questions regarding QMPs focus solely on the reporting of relevant measurement information. This assumption was deemed likely, since each replication within a set was based on the same protocol. Furthermore, the goal of these protocols is to ensure that the measurement practices are equal across the different replication studies of the same original effect.

To test hypothesis 4, the total QMP ratios between replication and original research was compared. The model formula for this test looked as follows:

INSERT H4 FORMULA HERE

Where $replication_{i}$ is a dummy coded variable, which was coded as 1 in case the reported QMP ratio belonged to a replications, and 0 if it belonged to an original study. For hypothesis 5 a similar formula was used:

INSERT H5 FORMULA HERE

Where $replicated_{i}$ is a dummy coded variable, which was coded as 1 if the meta-analytic effect in the replication set matches the original effect in direction at a significance alpha level of .05, and 0 otherwise. Note here that unlike in the test for hypothesis 4, $QMP\_ratio_{i}$ refers only to the QMP ratios of the replications, meaning that original article QMPs were not included in this analysis.

The relationship between original article QMPs and replication protocol QMPs was modelled to test hypothesis 6. The outcome variable remains the same as in the model for hypothesis 5. The independent variable is changed to the QMP ratio for original articles. The resulting model formula is as follows:

INSERT H6 FORMULA HERE

These models had independence of observations as another assumption, the observations here referring to a replication set. this is known to be false since the data is nested within four separate Many Labs projects. In order to test if this nested structure might influence the relations described in hypothesis 5 & 6, random intercept and random slope multilevel models were implemented as sensitivity analyses for the tests of both hypothesis 5 & 6. In these models each replication set was treated as being nested in its respective Many Labs project. Worth noting is that currently the betareg package does not allow for estimation of multilevel models. As an approximation, Gaussian random-intercept multilevel models were implemented using the lmer function from the lme4 package [@bates2015lme4]. The outcome QMP ratio variable was transformed using the logit link function (the default link function in the betareg package) to better fit the Gaussian model.

### Exploratory Analyses
Follow-up analyses were preregistered for hypothesis 6. Using a similar model to the main hypothesis test with all unique combination of the five different QMP types being tested across original and replication data. The goal of these analyses was to see if there are any type specific carry-over effects in QMPs between original and replication. As these analyses are exploratory in nature, due to the large number of tests, the focus was on visualisation rather than inference.

Finally, in order to present additional validity evidence alongside the analyses of Cronbach's alpha and omega coefficients, the unidimensionality of each measure was investigated. To test this, each multiple item scalar measure had their factor structure investigated on the entire measure data of the replication set. A single factor confirmatory factor analysis was implemented using the *fa* function from the *psych* package [@revelle2022psych] in R. The maximum likelihood factoring method was used, with defaults being used for all other function arguments. From this analysis, the RMSEA of the one factor solution was extracted. Additionally, a parallel test was conducted using the *fa.parallel* function also from the psych package. If either the RMSEA score < .08, or the parallel analysis returned a one factor solution, unidimensionality was coded as true, otherwise it was coded as false.
